---
title: "Conic Log-Binomial Regression"
author: Florian Schwendinger
output: md_document
---

# Conic Log-Binomial Regression

This **README** provides some additional details on the **lb** package.
The **lb** package was compiled to further the reproducibility
of the `Conic Log-Binomial Regression` paper.

## Simulations A
The simulation settings A can be reproduced by using the function
`simdata_blizhosm2006`.
```{r}
set.seed(0)
library(lb)

nobs <- 500L
setting <- 1L
d <- simdata_blizhosm2006(nobs, setting = setting)

s <- lb_convex(d$x, d$y)
betahat_1 <- setNames(as.double(s), sprintf("beta%i", seq_along(s) - 1L))
betahat_1

start <- lb:::lb_start(d$y, d$x)
s <- lb_coptim(d$x, d$y, start = start)
betahat_2 <- setNames(s$par, sprintf("beta%i", seq_along(s$par) - 1L))
betahat_2

s <- lb_auglag(d$x, d$y, start = start)
betahat_3 <- setNames(s$par, sprintf("beta%i", seq_along(s$par) - 1L))
betahat_3
```

## Simulations B
The simulation settings B can be reproduced by using the function
`simdata_savuliuyasui2009`.
```{r}
nobs <- 500L
setting <- 1L
d <- simdata_savuliuyasui2009(nobs, setting = setting)

s <- lb_convex(d$x, d$y)
betahat_1 <- setNames(as.double(s), sprintf("beta%i", seq_along(s) - 1L))
betahat_1

start <- lb:::lb_start(d$y, d$x)
s <- lb_coptim(d$x, d$y, start = start)
betahat_2 <- setNames(s$par, sprintf("beta%i", seq_along(s$par) - 1L))
betahat_2

s <- lb_auglag(d$x, d$y, start = start)
betahat_3 <- setNames(s$par, sprintf("beta%i", seq_along(s$par) - 1L))
betahat_3
```

## Simulations C
The simulation settings C can be reproduced by using the function
`sim_data_marschner_plus_minus`.
```{r}
nobs <- 500L
ncov <- 10L
d <- sim_data_marschner_plus_minus(nobs, ncov)

s <- lb_convex(d$x, d$y)
betahat_1 <- setNames(as.double(s), sprintf("beta%i", seq_along(s) - 1L))
betahat_1

start <- lb:::lb_start(d$y, d$x)
s <- lb_coptim(d$x, d$y, start = start)
betahat_2 <- setNames(s$par, sprintf("beta%i", seq_along(s$par) - 1L))
betahat_2

s <- lb_auglag(d$x, d$y, start = start)
betahat_3 <- setNames(s$par, sprintf("beta%i", seq_along(s$par) - 1L))
betahat_3
```

## References
Schwendinger F, Bettina Gruen, Hornik K (2020) Conic Log-Binomial Regression
